Ten Simple Rules for Teaching Programming

### 2017-07-09 paper.tex
Updating bibliography

The best method developed so far for larger-scale classrooms is called Peer Instruction.
Originally created by Eric Mazur at Harvard~\citep{mazur-peer-instruction},
it has been studied extensively in a wide variety of contexts,
including programming \citep{cutts,porter}.
In simplified form,
peer instruction proceeds in three phases:

@@

A classic question in computing (and mathematics) education is whether problems are better 
with context (e.g. find the highest student grade) or without (e.g. find the maximum of the list of numbers).
\citet{bouvier-context} studied this with a multi-university study and found no difference between
the two.  They suggest that since it makes no difference, other considerations (such as motivation)
should be primary.

One caution is that context can inadvertently exclude some people while drawing others in.
For example,
many educators use computer games as a motivating example for programming classes,
but some learners may associate them with violence and racial or gender stereotypes,
or simply find them unenjoyable.

\section{Novices are not experts}\label{not-experts}

>>>>

The best method developed so far for larger-scale classrooms is called Peer Instruction.
Originally created by Eric Mazur at Harvard~\citep{mazur-peer-instruction},
it has been studied extensively in a wide variety of contexts,
including programming \citep{porter-multi,porter-success}.
In simplified form,
peer instruction proceeds in three phases:

@@

A classic question in computing (and mathematics) education
is whether problems are better with context (e.g., find the highest student grade)
or without (e.g. find the maximum of the list of numbers).
\citet{bouvier-context} examined this with a multi-university study
and found no difference between the two.
They suggest that since it makes no difference,
other considerations (such as motivation) should be primary.

One caution is that context can inadvertently exclude some people while drawing others in.
For example,
many educators use computer games as a motivating example for programming classes,
but some learners may associate them with violence and racial or gender stereotypes,
or simply find them unenjoyable.
Whatever examples are chosen,
the goal must be to move learners as quickly as possible
from ``hard and boring'' to ``easy and exciting'' \cite{repenning}.

\section{Remember that novices are not experts}\label{not-experts}
